Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
typo
fix in appendices

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weights to preserve the unbiasedness of the gradient estimate.
        Under standard assumptions on the MDP, we provide convergence guarantees for SVRPG with a convergence rate that is linear under increasing batch sizes.
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

\begin{align*}
\vtheta^{s+1}_1 &= \wt{\vtheta}^s + \textbf{ADAM}\left(\wh{\nabla}_N J(\wt{\vtheta}^s),\beta_1,\beta_2,2\alpha\right),\\
\vtheta^{s+1}_{t+1} &= \textbf{ADAM}\Big( 
%        v_t^{s+1}
\blacktriangledown J(\vtheta^{s+1}_t),\beta_1,\beta_2,\alpha\Big)
\text{ for $t=1,\dots,m-1$},
\end{align*}

where separate histories are kept for estimated first moments $\kappa_{FG},\kappa_{IS}$ and estimated second moments $\nu_{FG},\nu_{IS}$.
The meta-parameters $\alpha,\beta_1,\beta_2$ are constant and set to default values or with minor manual tuning (see table \ref{table:metaparams}). Note that we double $\alpha$ for the snapshot ADAM since we can rely on a larger number of trajectories ($N$ instead of $B$) to control the variance.

>>>>

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weight to preserve the unbiasedness of the gradient estimate.
        Under standard assumptions on the MDP, we provide convergence guarantees for SVRPG with a convergence rate that is linear under increasing batch sizes.
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

\begin{align*}
\vtheta^{s+1}_1 &= \wt{\vtheta}^s + \textbf{ADAM}\left(\wh{\nabla}_N J(\wt{\vtheta}^s),\beta_1,\beta_2,\alpha\right),\\
\vtheta^{s+1}_{t+1} &= \textbf{ADAM}\Big( 
%        v_t^{s+1}
\blacktriangledown J(\vtheta^{s+1}_t),\beta_1,\beta_2,\frac{\alpha}{2}\Big)
\text{ for $t=1,\dots,m-1$},
\end{align*}

where separate histories are kept for estimated first moments $\kappa_{FG},\kappa_{IS}$ and estimated second moments $\nu_{FG},\nu_{IS}$.
The meta-parameters $\alpha,\beta_1,\beta_2$ are constant and set to default values or with minor manual tuning (see table \ref{table:metaparams}). Note that we double the sub-iterations' learning rate for the snapshot ADAM since we can rely on a larger number of trajectories ($N$ instead of $B$) to control the variance.
